\documentclass[11pt]{article}
\usepackage{array}
\usepackage[margin=12mm]{geometry}
\title{\bfseries \Huge Rolf Britten \\ \Large Curriculum Vitae}
\date{}
\pagenumbering{gobble}
\hyphenpenalty=1000
\exhyphenpenalty=1000
\begin{document}

\maketitle
\vspace{-10mm}
\begin{minipage}[ht]{0.48\textwidth}
\begin{tabular}{r l}
Tel: & (+44) 1234 123456\\
E-mail: & rolfbritten@gmail.com\\
\end{tabular}
\end{minipage}
\begin{minipage}[ht]{0.48\textwidth}
\begin{tabular}{l l}
& Address Line 1, Address Line 2\\
& Address Postcode\
\end{tabular}
\end{minipage}

\begin{center} \emph{ Part-qualified Actuary with a proven record of delivering high-quality analyses and project contributions. Experienced in Motor Risk Pricing with a particular interest in nascent pricing technologies and techniques.} \end{center}

\section*{Professional Experience}
\begin{description}

\item[AXA Insurance]: \\
\textbf{Senior Technical Pricing Analyst} \emph{January 2018 -- Present}\\
\textbullet \quad Involved throughout the delivery of new Machine Learning (ML) model suite. Main overseer of SAS data pipeline, eRate build, Impact Analysis and project retrospective. \\
\textbullet \quad Drove forward Motor Technical Pricing activities in manager's absence, including ML project, investigations into emerging pricing issues and securing committee buy-in for trial ramp up and tweaks. \\
\textbullet \quad Supported members of the team with technical problems and shared areas of knowledge I have gained from a large spectrum of pricing work. \\
\textbullet \quad Feature engineering from test-level MOT data, followed by analysis and presentation of statistically significant pricing deficiencies. \\
\textbullet \quad Developed a number of bespoke functions for in-house R package - including creation of PDP function and dynamic html MI packs - which were instrumental in communicating ML results to stakeholders. \\
\textbullet \quad Chairing regular meeting for cross-team analysts to present work and share knowledge. \\
\textbullet \quad End of year review rating of `Excellent'.
\\\\
\textbf{Technical Pricing Analyst} \emph{June 2015 -- December 2017}\\
\textbullet \quad Refresh of Motor Insurance EMBlem Risk Pricing models suite from SAS Data Prep to post-deploy analysis and monitoring. \\
\textbullet \quad Developed in-house alternative to market-leading geographic analysis tool in R. Incorporated several bespoke algorithms to compete/ensemble. Tool has been shared across business units, including overseas, with consistent improvement in performance on unseen data. \\
\textbullet \quad Examined claims development across rating factors and created bootstrap solution to assess significance of observed differences. \\
\textbullet \quad Wrote updated Motor Expected Loss Ratio (ELR) process. Integrated stochastic elements to produce confidence intervals on reported ELR to demonstrate to stakeholders variance of loss ratio predictions, especially over smaller business volumes. \\
\textbullet \quad End of year review ratings of `Excellent' and `Outstanding'.
\\\\
\textbf{eRate Analyst} \emph{April 2014 -- June 2015}\\
\textbullet \quad Received award from MD for delivering Group Internal Audit action to set up automated solution for testing of aggregator mappings against a tight deadline. This involved designing a solution from scratch and the delegation of work to peers.\\
\textbullet \quad Devised several highly effective changes to eRate processes - including digestible log of production rating models for stakeholders and Weekly Deploy Stand Up. \\
\textbullet \quad Proactively working with several areas of the business (such as pricing, projects and IT teams) in order to deliver accurate and timely pricing changes, small change, defect fixes and projects.\\
\textbullet \quad End of year review rating of `Excellent'.

%\item[Zurich Global Corporate UK]:\\
%\textsc{Work experience within Actuarial Reserving and Pricing teams} \emph{February 2014}\\
%Updated reserving spreadsheets and made preliminary estimates ready for incoming 2014 Q1 data.\\
%Analysed market data for models' rate change assumptions. Conducted initial analysis of new business's claims history.

\item[Buckinghamshire County Council - Legal \& Democratic Services]:\\
\textbf{Assistant Complaints Officer/Assistant Claims Handler:} \emph{Jun -- Aug 2012; Jul 2013 -- Mar 2014}\\
\textbullet \quad Processing and investigating public liability claims against the council. Repudiating claims or requesting settlement from contractors, based on evidence of due diligence/negligence. \\
\textbullet \quad Managing case files of high-level customer complaints and Ombudsman investigations to facilitate timely dispute resolution.

%\item[Buckinghamshire County Council - Legal \& Democratic Services] June 2012 - September 2012\\
%\emph{Administrative Assistant:}\\
%Providing business support to a legal team of 70 staff, including data mining from case management/time recording system and design of website to market services to clients. 
%\item[Budgens Bedgrove] March 2010 -- September 2011\\
%\emph{Team Member:} Processing customers' purchases, maintaining stock %levels and providing friendly customer service\\

\end{description}

\section*{Education}
\begin{tabular}{l | l l}
2016 --  & \textbf{Institute and Faculty of Actuaries} Part-qualified \\
& \hspace{4mm} \textit{CT1-9 - 77\% average, CA1} \\
2010 -- 2013 & \textbf{University of Exeter} BSc [Hons] Mathematics - 2:1\\
& \hspace{-2.8mm} \begin{tabular}{l l l}
& \textit{Advanced Statistical Modelling} & \textit{Stochastic Processes}\\
& \textit{Numerics and Optimisation} & \textit{Intro to Finance and Accounting}\\
& \textit{Mathematics Group Project} & \hspace{-8mm}\textit{(15,000 word report on Hurricane Trends)}
\end{tabular}\\
2008 -- 2010 & \textbf{Aylesbury Grammar School} A Level \\
& \hspace{4mm} \textit{Mathematics - A, Physics - A, German - B} \\
%2003 -- 2008 & \textbf{Aylesbury Grammar School} GSCE \\
%& \hspace{4mm} \textit{8 As, 3 Bs, 1 C}
\end{tabular}


\section*{Skills}
\begin{description}

\item[Technical Knowledge] I am highly proficient in SAS and R, experienced in VBA, SQL and Git version control. I have also taken online courses in Python and Java. \\
I am motivated by the challenge of coding solutions to business problems and am always looking to add to my technical skill set.

\item[Leadership and Communication] I enjoy working closely with others and mentoring more junior colleagues, helping them to understand and work on complex issues. My early career at AXA put me at the heart of many IT projects, introducing me to Agile project methodologies. I have taken many of pieces of work to various committees for approval or discussion and ran my own regular meeting, curating the agenda and modifying the format to give the most value to the analyst community.

\item[Innovation] I will always look to complete projects and ad-hoc work in a way that challenges and improves processes, where appropriate, without sacrifices to objective outcomes. Throughout my career at AXA I have made improvements to many processes across the eRate and Pricing team. Examples include  writing and sharing SAS macros to cut analyst time spent on repetitive work and rewriting code to improve run time, readability and accuracy -- such as the Motor ELR process.

\item[Pragmatism] The completion of the ML project encountered many obstacles where a perfect solution was out of scope. I had a key role in implementing the solution for `dual-scale' features and deriving an Impact Analysis where changes in premiums were outside the envelope of usual rate changes. I planned and delivered a proof of concept of a system for removal of old/personal data which will inform the approach taken when project returns in the coming year.

\item[Language Skills] Competent speaker of German and French.

\end{description} 

\section*{Interests}

Keen long-distance road cyclist. I have taken part in many charity cycle rides including AXA UK's cycle challenge for which I was a lead cyclist in charge of the safety and coherence of my group. Other interests include playing football, seeing music shows and film editing.\\

\noindent Charity Volunteer - assisting in the running of STAR's (Student Action for Refugees) annual conferences and training events.
I also organised an office collection of warm clothes to be sent to Train of Hope, an aid station in Vienna providing for refugees travelling across Europe.

%\section*{References available upon request}

\end{document}